Compositional equivalences based on Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-09-02 2016-Weak-FH-Bisim/WeakBisim.tex
suppress old proof

What we need now is an adaptation of Lemma~\ref{lem-rel-OT-WOT} where transitions are WOTs and not OTs ... \TODO{comment depending on the status of lemma 4 bis (Rabea). Thus by Lemma 4 bis:}
 We obtain:

@@

\TODO{Anciennement debut preuve equivalnec weak FH-bisimulation}

Consider 3 open automata 
       	$\mathcal{T}_1$, $\mathcal{T}_2$, $\mathcal{T}_3$ and states $s$, $t$, $u$ 
       	in those 
       	automata\footnote{We omit the constraints stating that each $s_x,\,t_x,\,u_x$ is 
       	in the 
       	states of 
       		$\mathcal{T}_1,\,\mathcal{T}_2,\,\mathcal{T}_3$ for the sake of readability}.
       	Suppose we have $\mathcal{R}$ an FH-bisimulation relation between states of 
       	$\mathcal{T}_1$ and of  $\mathcal{T}_2$; members of $\mathcal{R}$ are of the form 
       	$(s,t|\Pred_{s,t})$.
       	Suppose we also  have $\mathcal{R}'$ an FH-bisimulation relation between states 
       	of 
       	$\mathcal{T}_2$ and of  $\mathcal{T}_3$; members of $\mathcal{R}'$ are of the 
       	form 
       	$(t,u|\Pred_{t,u})$.

       	We will show
       	that $\mathcal{R}''$ is an FH-bisimulation. Consider 
       	$(s,u|\Pred_{s,u})\in\mathcal{R}''$. Then there is a set of states of 
       	$\mathcal{T}_2$ relating $s$ and $u$, let $(t_p)^{p\in P}$ be this family.  
       	       	We have $\Pred_{s,u} = \bigvee_{p\in P} \Pred_{s,p}\land\Pred_{p,u}$.

       	For any $p\in P$ by definition of $\mathcal{R}''$,
       	$(s,t_p|\Pred_{s,p})\in\mathcal{R}$,  and 
       	$(t_p,u|\Pred\,'_{p,u})\in\mathcal{R}'$. 
       	We have 
       	the 
       	following by definition of bisimulation:
For any $p\in \mathcal{S}_2$ by definition of $\mathcal{R}''$, $(s,p|\Pred_{s,p})\in\mathcal{R}$,  and $(p,u|\Pred_{p,u})\in\mathcal{R}'$. 
We have the following by definition of weak bisimulation:\\
For any open transition $OT$ in $\mathcal{T}_1$ originating from $s$.
       	\begin{mathpar}
       	\openrule
       	{
       		\beta_j^{j\in J_1},\Pred_{OT},\Post_{OT}}
       	{s \OTarrow {\alpha} {s}'}  \qquad (1)   	
       	\end{mathpar}

       	There exist weak open transitions $OT_{px}^{x\in X} \subseteq \mathcal{T}_2$:

       	\begin{mathpar} 
       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
       	\openrule
       	{
       		\gamma_{jpx}^{j\in J_{px}}, \Pred_{OT_{px}},\Post_{OT_{px}}}
       	{t \OTWeakarrow {\alpha_{px}} t_{px}}\qquad (2)
       	%         \right)
       	\end{mathpar}

       	such that  $\forall x, \{j\in J_1|\beta_j \neq \tau\}=J_{x}, (s',t_{px}|\Pred\,_{s'\!,{px}})\in 
       	\mathcal{R}$;
       	and  \\

       	$\Pred_{s,p} \land \Pred_{OT}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       	\left( \forall j. \vis{\beta_j}=\gamma_{jx}  \Rightarrow \Pred_{OT_{px}}
       	\land \alpha\!=\!\alpha_{px} \land
       	\Pred\,_{s'\!,{px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)$\\

       	\begin{mathpar}  	
       	%    \left( fresh \ \set{a_i}, \set{b_j}, v_x.\ \
       	\openrule
       	{
       		\gamma_{jpxy}^{j\in J_{pxy}}, 
       		\Pred_{OT_{pxy}},\Post_{OT_{pxy}}}
       	{u \OTWeakarrow {\alpha_{pxy}} u_{pxy}}\qquad (3)
       	%         \right)    	
       	\end{mathpar}
       	such that  $\forall y, J_{px}=J_{pxy}, 
       	(t_{px},u_{pxy}|\Pred_{{px,pxy}})\in \mathcal{R}'$; and  \\
       	$\Pred_{p,u} \land \Pred_{OT_{px}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. \vis{\beta_{jpx}}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\

This is verified for all $p \in P$. Overall,  we have a family of open 
       	transitions 
       	$OT_{xy}^{p\in P, x\in X, 
       		y\in Y} \subseteq \mathcal{T}_3$ that should simulate \emph{OT}.

------------------------------------------------------------------

We have  $\forall y, \forall x, \forall p \in P,  \{j \in J_1|\,\beta_j\neq \tau\} =J_{px}=J_{pxy}, 
       	({s}',u_{pxy}|\Pred_{s',{pxy}})\in \mathcal{R}''$ for some $\Pred_{{s',pxy}}$.  Indeed,  for any $p$, $x$ and $y$,  we have
$(s',t_{px}|\Pred_{{s'\!,px}})\in \mathcal{R}$
       	and $(t_{px},u_{pxy}|\Pred_{{px,pxy}})\in \mathcal{R}'$. For states ensuring the transitivity relation we have   
       		 for all $p$, $x$, $y$, $\Pred_{px}\land 
       	\Pred_{{px,pxy}}\implies 
       	\Pred_{{s'\!,pxy}}$.

\TODO{We need to prove that we have the following  relation:}  \\     	
       	\begin{small}
 $\Pred_{s,u} \land \Pred_{OT}\\
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!\bigvee_{p\in P}
       		\left( \forall j. \vis{\beta_j}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       		\land \alpha\!=\!\alpha_{pxy} \land
       		\Pred_{{s',\!xy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\right)$.
       	\end{small}

\noindent By rule given in (2) we have for all $p$:\\
\begin{small}
$\big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
       		\hspace{1cm} \implies\!\!\! \Big(\bigvee_{x\in X}
       		\left( \forall j. \vis{\beta_j}=\gamma_{jpx}  \Rightarrow \Pred_{OT_{px}}
       		\land \alpha\!=\!\alpha_{px} \land
       		\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\right)\Big)\land\Pred_{p,u}\\
       		%
       		\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!
       	\Big( \forall j.\vis{\beta_j}\!=\!\gamma_{jpx}  \Rightarrow 
       		(\Pred_{OT_{px}}\land\Pred_{p,u})
       		\land \alpha\!=\!\alpha_{px} \land
       		\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\Big).\\
       		%
       		$
  \end{small}

\noindent By rule given in (3) we have:   \\
$\Pred_{p,u} \land \Pred_{OT_{px}}\\
       	\hspace{1cm} \implies\!\!\! \bigvee_{y\in Y}
       	\left( \forall j. \gamma_{jpx}=\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
       	\land \alpha_{px}\!=\!\alpha_{pxy} \land
       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)$.\\

\noindent So can rewrite the formula as:\\	
\begin{small}
$ \big(\Pred_{s,p} \land \Pred_{OT}\big)\land\Pred_{p,u}\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}
       	\bigg( \forall j.\vis{\beta_j}\!=\!\gamma_{jpx}  \Rightarrow\\~~\hspace{2em}
       		\Big(\!\bigvee_{y\in Y}
       			\left( \forall j'. \gamma_{j'px}\!=\!\gamma_{j'pxy}  \Rightarrow \Pred_{OT_{pxy}}\!\land \alpha_{px}\!=\!\alpha_{pxy}
\land \Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\right)   \Big)\\~~ \hspace{2em} \land \alpha\!=\!\alpha_{px} \land
       		\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\bigg).\\
\hspace{1cm}\implies\!\!\!\!\bigvee_{x\in X} \bigvee_{y\in Y}\bigg(\forall j, j'.\vis{\beta_j}\!=\!\gamma_{jpx}\!\land\!\gamma_{j'px}\!=\!\gamma_{j'pxy}
 \Rightarrow\\~~\hspace{2em} \Big(\Pred_{OT_{pxy}}\!\land\alpha\!=\alpha_{px}\!=\!\alpha_{pxy} \land 
       \Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
       		\land
\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\Big)\bigg).
       		$
       \end{small}

\medskip
\noindent Because of variables domains independence we  have:\\ 
    $\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\land 
       	\Pred_{{px,pxy}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}
       	\Leftrightarrow\\ % we changed =
\Pred_{{s'\!,px}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}}\land
       \Pred_{{px,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}} \Leftrightarrow
\big(\Pred_{{s'\!,px}} \land   \Pred_{{px,pxy}}\big)   \subst{\Post_{OT}}\subst{\Post_{OT_{px}}}\subst{\Post_{OT_{pxy}}} \\	\implies\Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{px}}}
\subst{\Post_{OT_{pxy}}}\Leftrightarrow  \Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}} $\\

\noindent This allows us to conclude with $\Pred_{s,u} = \bigvee_{p\in P} 
       	\Pred_{s,p}\land\Pred_{p,u}$:

      	\begin{small}     	
$\Pred_{s,u} \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\! \bigvee_{p\in P} \big(
	\Pred_{s,p}\land\Pred_{p,u}\big) \land \Pred_{OT}\\
\hspace{1cm} \implies\!\!\!\bigvee_{p\in P}\bigg(\!\!
 \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!
\Big( \forall j, j'.\vis{\beta_j}\!=\!\gamma_{jpx} \land \gamma_{j'px}\!=\!\gamma_{j'pxy}\Rightarrow\\~~\hspace{2em}
\Big( 
\Pred_{OT_{pxy}}
\land \alpha\!=\alpha_{px}\!=\!\alpha_{pxy} \land
\Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\Big)\Big)\bigg)
\\
\hspace{1cm} \implies\!\!\! \bigvee_{x\in X}\!\!\bigvee_{y\in Y}\!\!\bigvee_{p\in P}\!\!
\Big(\forall j.\vis{\beta_j}\!=\!\gamma_{jpxy}  \Rightarrow \Pred_{OT_{pxy}}
\land\, \alpha\!=\!\alpha_{pxy} \land
\Pred_{{s'\!,pxy}}\subst{\Post_{OT}}\subst{\Post_{OT_{pxy}}}\Big)$.
  \end{small}

>>>>

By definition of weak open transition (Definition~\ref{def:buildweakOT}),
 we obtain:

@@
